\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{color}
\setlength{\topmargin}{-0.3 true in}
\setlength{\headsep}{0 true in}
\setlength{\topskip}{0 true in}
\setlength{\textwidth}{6.5 true in}
\setlength{\oddsidemargin}{0 true in}
\setlength{\evensidemargin}{0 true in}
\setlength{\textheight}{9.2 true in}
\renewcommand{\arraystretch}{1.2}
\newcommand{\eps}{\varepsilon}
\newcommand{\R}{{\mathbb R}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\Z}{{\mathbb Z}}
\theoremstyle{definition}
\newtheorem{problem}{Problem}
\definecolor{darkblue}{RGB}{0,0,150}
\definecolor{darkred}{RGB}{180,0,0}
\definecolor{darkgreen}{RGB}{0,120,0}
%\newenvironment{answer}{\par\medskip\bgroup\color{darkblue}\noindent\textbf{Answer:}\par\medskip}{\egroup\medskip}
\newenvironment{answer}{\par\medskip\bgroup\color{darkblue}}{\egroup\medskip}
\newenvironment{grading}{\par\medskip\bgroup\color{darkred}}{\egroup\medskip}
\newenvironment{secondans}{\par\medskip\bgroup\color{darkgreen}}{\egroup\medskip}
\newcommand{\grd}[1]{{\color{darkred}#1}}
\pagestyle{empty}


\begin{document}

\hbox to \hsize{\textbf{Math 331, Fall 2022\hfill Homework 5}}
\nointerlineskip
\vskip 2pt
\hrule height 1pt

\medskip

\centerline{\textit{This homework on Metric Spaces is due Friday, October 7}}

\bigskip

\def\ds{\displaystyle}


\begin{problem}  % problem 1
Let $(M,d)$ be a metric space, and let $A$ be a subset of $M$.  Prove that $A$ is open
if and only if $A$ is equal to a union of open balls.
\end{problem}

\begin{answer}
%You can put your answer here, 4 points
\end{answer}


\begin{problem}  % problem 2
Consider the metric space $(\R,d)$, where $d$ is the usual metric on $\R$  For each $n=1,2,3,\dots,$ let ${\cal O}_n$ be 
the open set ${\cal O}_n=\big(1,1+\frac{1}{n}\big).$
Show that $\{{\cal O}_n\,|\,n=1,2,\dots\}$ is an infinite collection of open
sets whose intersection is not open.
And find an infinite collection of closed subsets of $(\R,d)$ whose union is not closed.
\end{problem}

\begin{answer}
%You can put your answer here, 3 points
\end{answer}


\begin{problem}  % problem 3
Let $X$ be any non-empty, bounded subset of $\R$, and let $\lambda$ be the least upper bound
of $X$.  Show that $\lambda\in\overline{X}$.  That is, the least upper bound of any set is an
element of the closure of that set.  [Hint:  Use the definition of closure of $X$ as the set of all
points of $X$ plus all accumulation points of $X$, and use Problem~1 from Homework~3.]
\end{problem}

\begin{answer}
%You can put your answer here, 3 points
\end{answer}



\begin{problem}  % problem 4
Let $(A,\sigma)$, $(B,\tau)$, and $(C,\eta)$ be metric spaces.  Let $f\colon A\to B$ and $g\colon B\to C$.
Suppose that $f$ and $g$ are continuous functions.  Prove that their composition, $g\circ f$, is a continuous
function.
\end{problem}

\begin{answer}
%You can put your answer here, 3 points
\end{answer}


\begin{problem}  % problem 5
Let $\{x_n\}_{n=1}^\infty$ be a convergent sequence in a metric
space.  Show that its limit is unique.  That is, prove the following statement:
if $\{x_n\}_{n=1}^\infty$ converges to $y$ and 
$\{x_n\}_{n=1}^\infty$ converges to $z,$ then $y=z$.
\end{problem}

\begin{answer}
%You can put your answer here, 2 points
\end{answer}

\end{document}
